### 2014-08-27 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg 2014 Report: Added author, changed figure names
Spartanburg: update image name and report
Spartanburg 2014: Add 286 College Test Descriptions to report appendix

\headerC{
{
\flushright{
Daniel Madrzykowski \\
Kristopher J. Overholt \\
Craig G. Weinschenk \\

@@

\headerC{
\flushright{
Daniel Madrzykowski \\
Kristopher J. Overholt \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_1st_Floor}
\caption{Instrumentation, 305 Manning, first floor}
\label{fig:Instrumentation_305_Manning_1st_Floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_2nd_Floor}
\caption{Instrumentation, 305 Manning, second floor}
\label{fig:Instrumentation_305_Manning_2nd_Floor}
\end{figure}

@@

@@

@@

@@

>>>>

\headerC{
{
\flushright{
Daniel Madrzykowski \\
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Keith M. Stakes \\

@@

\headerC{
\flushright{
Daniel Madrzykowski \\
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Keith M. Stakes \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_1st_Floor}
\caption{Instrumentation, 289 Manning, first floor}
\label{fig:Instrumentation_289_Manning_1st_Floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_Basement}
\caption{Instrumentation, 289 Manning, basement}
\label{fig:Instrumentation_289_Manning_basement}
\end{figure}

@@

The first set of experiments were conducted in a single story residential structure with attached garage addressed as 286 College Street.  The structure consisted of type 5 construction. The attached garage was added on to the B side of the structure for the purpose of these tests.  The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.  The burn rooms had a combustible finish comprised of OSB sheets for wall linings.  Three tests were conducted in this structure: 1) A living room fire with a residential sprinkler present, 2) An attached garage fire with exterior attack, and 3) A living room fire with door control.

@@

Test 1 consisted of a fire in the living room with residential sprinkler activation.  Ignition occurred on a couch in the living room to the rear of the structure near the C/D corner.  The fire was remotely ignited from the exterior of the structure.  There was a residential sprinkler in the fire room.  Other fire room furnishings included a sofa chair, two wooden end tables, a floor lamp, cloth window curtains, carpeted floor, and wooden paneling for wall linings.  The fire grew uninhibited until the sprinkler activated and suppressed the bulk of the fire.  A fire fighting crew made entry through side C for mop-up.

@@

Test 2 consisted of a fire in the attached garage with an exterior fire attack.  Two separate ignition points were used, one of which was inside a car located in the garage and another was located on a couch to the rear of the garage.  The couch simulated other fuel loads commonly found within a garage.  Several wooden pallets were also placed in the garage for additional fuel.  The fire was ignited remotely from the exterior of the garage.  The door from the attached garage to the interior of the structure (kitchen area) remained closed for the duration of this test.  The fire grew uninhibited in the garage until the space reached flashover conditions and became fully-involved.  The fire was knocked down and suppressed from the exterior of the structure by a fire fighting crew with a single hand-line in a straight stream pattern.  The front door on Side A of the structure was then opened to simulate a crew making entry.

@@

Test 3 consisted of a fire in the living room located in the front of the structure near the A/B corner.  The ignition point for this test was the corner of a modern-style couch and was performed remotely from the exterior of the structure.  Other fuels present in the room were another modern-style sofa and a modern-style love seat.  The fire room was lined with OSB paneling for additional fuel.  The front side A door was in the open position for the start of the test.  The target room, located adjacent to the fire room near the A/D corner, was separated by a closed hollow core wooden door.  Once ignited, the fire grew uninhibited until the room approached flashover conditions.  Prior to this, the front door to the room was closed.  The fire was allowed to stabilize and then the front door was opened.  The fire fighting crew made an attack from the exterior via a straight stream pattern from a single hand-line.  The pattern was then switched to a narrow fog for further suppression.  The fire fighting crew then made entry into the fire room for mop-up procedures.
